Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-17 paper.qmd
Do not need quollr to run the paper

if (!requireNamespace("quollr", quietly = TRUE)) {
  remotes::install_github("JayaniLakshika/quollr")
}

@@

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
library(quollr)
library(tibble)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(patchwork)
library(colorspace)
library(kableExtra)
library(conflicted)
library(ggbeeswarm)
library(scales)

@@

```{r}
#| label: tbl-links
#| tbl-pos: H
#| tbl-cap: "Videos of the langevitour animations and the linked plots."
# Video links in the paper

>>>>

@@

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
library(tibble)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(patchwork)
library(colorspace)
library(kableExtra)
library(conflicted)
library(ggbeeswarm)
library(scales)

@@

```{r}
#| label: tbl-links
#| tbl-cap: "Videos of the langevitour animations and the linked plots."
# Video links in the paper
